cardinalR: Generating interesting high-dimensional data structures

### 2025-08-23 paper-cardinalR.Rmd
Added Mobius data

```{r, eval=FALSE}
langevitour::langevitour(mobius)
```

@@

```{r, label = "fig-mobius-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `mobius` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r scurve, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `scurve` data in $4\\text{-}D$."}

>>>>

```{r}
mobius_lang <- langevitour::langevitour(mobius, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r mobius, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `mobius` data in $4\\text{-}D$."}

mobiusfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    mobius_lang
  ),
  device = "xs"
)

class(mobiusfig) <- c(class(mobiusfig), "htmlwidget")

mobiusfig
```

```{r mobius-proj, fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `mobius` data."}
#| fig-width: 15
#| fig-height: 5

@@

```{r scurve, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `scurve` and `scurvehole` data in $4\\text{-}D$."}

### 2025-08-23 paper-cardinalR.tex
Added Mobius data

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-mobius-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `mobius` data.}\label{fig:fig-mobius-proj}
\end{figure}

>>>>

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/mobius-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `mobius` data.}\label{fig:mobius-proj}
\end{figure}
